 Total Team Spending and Profitability Leads Results in a Higher League Ranking in the English Premier League

### 2024-04-03 paper/paper.qmd
Committing titles changes to paper.qmd and paper.pdf

---
title: "Predicting English Premier League Rankings in Relation to Total Team Spending in the 2023-2024 Season"
subtitle: "My subtitle if needed"
author: 
  - Isabella MacLean
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: " Total Team Spending and Profitability Leads Results in a Higher League Ranking in the English Premier League"
subtitle: "An Analysis of Economic Predictors on League Rank in the 2023-2024 Season"
author: 
  - Isabella MacLean
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
